---
output:
  md_document:
    variant: markdown_github
  pdf_document: default
  html_document: default
---
## GO (BP) enrichment with DAVID

```{r results='hide', message=F}
require(magrittr)
require(DOSE)
require(RDAVIDWebService)
require(clusterProfiler)
```

```{r eval=F}
load("cache/gene.rda")
david_bp4 <- enrichDAVID(gene, idType="ENSEMBL_GENE_ID", annotation="GOTERM_BP_ALL", david.user="gcyu@connect.hku.hk")
save(david_bp4, file = "david_bp4.rda")
```

```{r echo=F}
load("cache/david_bp.rda")
```

```{r fig.width=7, fig.height=7, fig.align='center'}
summary(david_bp)[, -8]
dotplot(david_bp, showCategory=12)
```

## GO (BP) enrichment with clusterProfiler



```{r echo=F}
load("cache/clusterProfiler_bp.rda")
```

```{r fig.width=10, fig.height=10}
dim(summary(clusterProfiler_bp))
head(summary(clusterProfiler_bp)[, -8])
dotplot(clusterProfiler_bp, showCategory=20)
```

```{r echo=F}
load("cache/clusterProfiler_bp4.rda")
```

```{r eval=F}
eg=bitr(gene, "ENSEMBL", "ENTREZID", "org.Hs.eg.db")[, "ENTREZID"]
clusterProfiler_bp4 <- enrichGO(eg, ont="BP", OrgDb = org.Hs.eg.db)
```


```{r fig.width=10, fig.height=10}
dim(clusterProfiler_bp4)
head(clusterProfiler_bp4[, -8])
dotplot(clusterProfiler_bp4, showCategory=20)
```


## Compare GO (BP) enrichment result obtained from DAVID and clusterProfiler
```{r fig.width=10, fig.height=10}
merge_result(list(david=david_bp, clusterProfiler=clusterProfiler_bp, clusterProfiler4=clusterProfiler_bp4)) %>%
    dotplot(., showCategory=10)
```

```{r}
summary(david_bp)[, "ID"] %in% summary(clusterProfiler_bp)[, "ID"]
```

+ DAVID only annotate 168 genes, while clusterProfiler can annotate 194 genes of the gene list with 207 genes in total.
+ DAVID enrich `r nrow(summary(david_bp))` BP terms, while clusterProfiler enrich `r nrow(summary(clusterProfiler_bp))` BP terms.
+ All enriched terms reported in DAVID were also reported by clusterProfiler. 


## Session info
```{r}
date()
sessionInfo()
```
