---
output:
  md_document:
    variant: markdown_github
  html_document: default
  pdf_document: default
---
## KEGG enrichment with DAVID

```{r results='hide', message=F}
require(magrittr)
require(DOSE)
require(RDAVIDWebService)
require(clusterProfiler)
```

```{r eval=F}
load("cache/gene.rda")
david_KEGG4 <- enrichDAVID(gene, idType="ENSEMBL_GENE_ID", annotation="KEGG_PATHWAY", david.user="gcyu@connect.hku.hk")
save(david_KEGG4, file = "david_KEGG4.rda")
```

```{r echo=F}
load("cache/david_KEGG.rda")
```

```{r fig.width=7, fig.height=7, fig.align='center'}
summary(david_KEGG)[, -8]
```

Ribosome is the only term reported by DAVID consistent with the result reported in the supplemental file.

## KEGG enrichment with clusterProfiler

```{r eval=F}
eg=bitr(gene, "ENSEMBL", "ENTREZID", "org.Hs.eg.db")[, "ENTREZID"]
clusterProfiler_KEGG4 <- enrichKEGG(eg)
save(clusterProfiler_KEGG4, file = "clusterProfiler_KEGG4.rda")
```

```{r echo=F}
load("cache/clusterProfiler_KEGG.rda")
```

```{r fig.width=10, fig.height=10}
dim(summary(clusterProfiler_KEGG))
head(summary(clusterProfiler_KEGG)[, -8])
dotplot(clusterProfiler_KEGG, showCategory=9)
```

```{r echo=F}
load("cache/clusterProfiler_KEGG4.rda")
```

```{r fig.width=10, fig.height=10}
dim(clusterProfiler_KEGG4)
head(clusterProfiler_KEGG4[, -8])
dotplot(clusterProfiler_KEGG4, showCategory=9)
```

## Compare KEGG enrichment result obtained from DAVID and clusterProfiler
```{r fig.width=10, fig.height=10}
merge_result(list(david=david_KEGG, clusterProfiler=clusterProfiler_KEGG, clusterProfiler4=clusterProfiler_KEGG4)) %>%
    dotplot(., showCategory=10)
```


+ DAVID's KEGG annotate 5085 genes in background while clusterProfiler use latest online version that annotate 6895 genes.
+ DAVID only annotate 83 genes, while clusterProfiler can annotate 104 genes of the gene list with 207 genes in total.
+ DAVID enrich `r nrow(summary(david_KEGG))` KEGG terms, while clusterProfiler enrich `r nrow(summary(clusterProfiler_KEGG))` KEGG terms.
+ All enriched terms reported in DAVID were also reported by clusterProfiler. 


## Session info
```{r}
date()
sessionInfo()
```
